---
title: "Part 1 MLR Lab"
author: "Elena Ortiz"
date: "12/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(stargazer)
```

```{r}
penguins %>% 
  ggpairs()
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```
## Build a few different models

```{r}
lm1 <- lm(body_mass_g ~ flipper_length_mm + species, data = penguins)

lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

lm3 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm, data = penguins)

lm4 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm + island, data = penguins)

```

## Find AIC value for each model

```{r}
AIC(lm1)
AIC(lm2)
AIC(lm3) # lowest value
AIC(lm4) # back up by adding variable island, might not be worth it 
```

Diagnostics

```{r}
plot(lm3)
```

Can be helpful to present the results of multiple models because it can be hard to choose which model to use

## Use stargazer package for a table with multiple model outputs

```{r, results = 'asis'}
stargazer(lm1, lm3, lm4, type = "html")

```

## Omitted variable bias

Simpson's Paradox example, leave out species
```{r}
ggplot(data = penguins, aes(x= flipper_length_mm, y = bill_depth_mm)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Adding species, we see the relationship correlation is reversed below. 
```{r}
ggplot(data = penguins, aes(x= flipper_length_mm, 
                            y = bill_depth_mm,
                            group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

